### 2020-03-24 paper/approach.tex
Edits all forms of SphinxES, \Sphinxes, \ac{Sphinx} etc.

After the initial, out-of-band setup, file transfer happens along
onion routes with the following features:\\
\textbf{Stateless.} There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. \\
 \textbf{Predictive.} The choice of which nodes is placed in which onion routing
  layer is informed on a predictive model for availability, disseminated
  by an overlay and queried by random peer sampling (RPS). Note that availability predictions only influence how nodes returned by the random peer sampling service are distributed among layers, but have no impact on the overall population of nodes making up the onion route. This population is controlled by the random peer sampling service, which we assume is secure. This is important to ensure strong privacy protection, and we return to this point in the Security Discussion of Section~\ref{security-discussion}.\\
 \textbf{Probabilistic.} Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way,
  resulting in a source-bounded random walk.\\
 \textbf{Onion Routing.} Put simply, in onion routing, the sender creates
  a source route and encapsulates the payload and next-hop information in layers (by
  encryption), that are \emph{peeled} (decrypted) one by one along the
  route. By virtue of these layers, the forwarding nodes on the
  route do not know where on the route they are and thus whether they
  have received a packet directly from the sender or some other
  intermediate node. We base our format for layering and peeling on the
  \ac{Sphinx} mix-header format, which we extend to allow for the
  changes above, described in \cref{Sphinxes}.

% \begin{description}
% \item [Stateless.] There is no mandatory circuit creation, the file transfer can be
%   done in a stateless way. 
% \item [Predictive.] The choice of nodes included in the onion routing
%   layers is based on a predictive model for availability, disseminated
%   by an overlay and queried by random peer sampling.
% \item [Probabilistic.] Instead of source routes with one node per onion layer, each
%   layer consists of a set of nodes and although the source route still
%   determines the sequence of layers, the actual node used for the next
%   hop of forwarding is selected from the set in an ad-hoc way,
%   resulting in a source-bounded random walk.
% \item[Onion Routing.] Put simply, in onion routing, the sender creates
%   a source route and 
%   encapsulates the payload and next-hop information in layers (by
%   encryption), that are \emph{peeled} (decrypted) one by one along the
%   route. By virtue of these layers, the forwarding nodes on the
%   route do not know where on the route they are and thus whether they
%   have received a packet directly from the sender or some other
%   intermediate node. We base our format for layering and peeling on
%   \ac{Sphinx}, with some modification to allow for the
%   changes above, described in \cref{Sphinxes}.
% \end{description}

@@

As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}). \ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploits decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
%% Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
%% \sonja{do we apply all categories here?} \ac{Sphinx} mix-header format.
%% This means that we inherit some properties from \ac{Sphinx} and due to being only a 
%% header format, it only imposes some restrictions in the above categories.
\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as \ac{Sphinx}, unidirectional (network structure), 
message-based (performance) communication.
But unlike \ac{Sphinx}, \Sphinxes is an hybrid source-hop-by-hop routed, and a
source-bounded random walk (communication 
model). \Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set just as she can learn the single node constituting a layer of a
secure onion-routing scheme without endangering the security
properties~\cite{CLOnionRouting}).

\Sphinxes does \emph{not} introduce any restrictions on whether the network 
topology must be fully connected or not, be asynchronous (as in \ac{Tor}) or 
synchronous (as in mix-nets), whether node selection must be uniformly random 
or not.
Just as \ac{Sphinx}, it can be used in many different settings.

Further, the \ac{SPOR} protocol (\cref{design}) adds node selection on top of \Sphinxes.
The \ac{SPOR} protocol (Figure~\ref{fig:outline} \ding{203})  assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
scheme~\cite[\eg][]{Octopus}.
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
\commentFT{What follows seems quite convoluted, with a lot of repetition. Would be nice to revise.} As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

>>>>

After the initial, out-of-band setup, file transfer happens along
onion routes with the following features:\\
\textbf{Stateless.} There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. \\
 \textbf{Predictive.} The choice of which nodes is placed in which onion routing
  layer is informed on a predictive model for availability, disseminated
  by an overlay and queried by random peer sampling (RPS). Note that availability predictions only influence how nodes returned by the random peer sampling service are distributed among layers, but have no impact on the overall population of nodes making up the onion route. This population is controlled by the random peer sampling service, which we assume is secure. This is important to ensure strong privacy protection, and we return to this point in the Security Discussion of Section~\ref{security-discussion}.\\
 \textbf{Probabilistic.} Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way,
  resulting in a source-bounded random walk.\\
 \textbf{Onion Routing.} Put simply, in onion routing, the sender creates
  a source route and encapsulates the payload and next-hop information in layers (by
  encryption), that are \emph{peeled} (decrypted) one by one along the
  route. By virtue of these layers, the forwarding nodes on the
  route do not know where on the route they are and thus whether they
  have received a packet directly from the sender or some other
  intermediate node. We base our format for layering and peeling on the
  \ac{Sphinx} mix-header format, which we extend to allow for the
  changes above, described in \cref{SphinxES}.

% \begin{description}
% \item [Stateless.] There is no mandatory circuit creation, the file transfer can be
%   done in a stateless way. 
% \item [Predictive.] The choice of nodes included in the onion routing
%   layers is based on a predictive model for availability, disseminated
%   by an overlay and queried by random peer sampling.
% \item [Probabilistic.] Instead of source routes with one node per onion layer, each
%   layer consists of a set of nodes and although the source route still
%   determines the sequence of layers, the actual node used for the next
%   hop of forwarding is selected from the set in an ad-hoc way,
%   resulting in a source-bounded random walk.
% \item[Onion Routing.] Put simply, in onion routing, the sender creates
%   a source route and 
%   encapsulates the payload and next-hop information in layers (by
%   encryption), that are \emph{peeled} (decrypted) one by one along the
%   route. By virtue of these layers, the forwarding nodes on the
%   route do not know where on the route they are and thus whether they
%   have received a packet directly from the sender or some other
%   intermediate node. We base our format for layering and peeling on
%   \ac{Sphinx}, with some modification to allow for the
%   changes above, described in \cref{SphinxES}.
% \end{description}

@@

As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}). \ac{SPOR} in turn combines a multi-set mix-header format (SphinxES) together with a node selection protocol that exploits decentralized prediction regarding node availability to optimize the reliability of SphinxES without jeopardizing its security properties.
%% Particularly, \sphinxes (\cref{SphinxES}), is an adaptation of the 
%% \sonja{do we apply all categories here?} \ac{Sphinx} mix-header format.
%% This means that we inherit some properties from \ac{Sphinx} and due to being only a 
%% header format, it only imposes some restrictions in the above categories.
SphinxES (Figure~\ref{fig:outline} \ding{202}) provides, just as \ac{Sphinx}, unidirectional (network structure), 
message-based (performance) communication.
But unlike \ac{Sphinx}, SphinxES is an hybrid source-hop-by-hop routed, and a
source-bounded random walk (communication 
model). SphinxES relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
SphinxES also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set just as she can learn the single node constituting a layer of a
secure onion-routing scheme without endangering the security
properties~\cite{CLOnionRouting}).

SphinxES does \emph{not} introduce any restrictions on whether the network 
topology must be fully connected or not, be asynchronous (as in \ac{Tor}) or 
synchronous (as in mix-nets), whether node selection must be uniformly random 
or not.
Just as \ac{Sphinx}, it can be used in many different settings.

Further, the \ac{SPOR} protocol (\cref{design}) adds node selection on top of SphinxES.
The \ac{SPOR} protocol (Figure~\ref{fig:outline} \ding{203})  assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
scheme~\cite[\eg][]{Octopus}.
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
\commentFT{What follows seems quite convoluted, with a lot of repetition. Would be nice to revise.} As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

### 2020-03-24 paper/intro.tex
Edits sphinxes and sphinxes-security
Edits all forms of SphinxES, \Sphinxes, \ac{Sphinx} etc.

First, we provide an extension to the Sphinx mix-header format~\cite{Sphinx} 
that adds several nodes per layer.
We call this extension SphinxES.
In essence, this makes it a source-routed random-walk.

@@

  \item We propose \Sphinxes, an extension of the
    \ac{Sphinx} mix-header format to set-based onion routing. \Sphinxes allows each layer of an onion route to contain several alternative next nodes, thus realizing a source-routed limited random-walk protocol.

  \item Building on \Sphinxes, we introduce the \ac{SPOR} %% node selection strategy for routing
    protocol
    that, given a secure 
    \ac{RPS} protocol and availability estimates, selects nodes to populate the 
    layers of \Sphinxes in order to maximize the availability of the route. This node selection procedure 
    yields reliable routes even in the presence of low-availability nodes while retaining the strong privacy properties of onion routing.

  \item We provide a protocol for a device \squad to estimate the availabilities 
    of its own devices, based on Markov models and \squad overlays.
    These estimated availabilities can then be exploited by \ac{SPOR} to populate \Sphinxes.
   % \commentDaniel{We should add some more details, maybe.}

@@

The remainder of this paper is organized as follows. Section~\ref{system-model} presents the
system and adversary models as well as the desired security and
privacy properties of \name. Section~\ref{approach} describes the
overall approach. In Section~\ref{Sphinxes}, we introduce \sphinxes. 
Then, in Section~\ref{design}, we introduce the different building
blocks of \name. In sections~\ref{security-discussion} and \ref{Performance},
respectively, we evaluate the security and performance of our
approach. We set \name into context with related work in
Section~\ref{RelatedWork}, and finally conclude with Section~\ref{conclusion}.

>>>>

First, we provide an extension to the Sphinx mix-header format~\cite{Sphinx} 
that adds several nodes per layer.
We call this extension SphinxES and describe it in detail in \cref{SphinxES}.
In essence, this makes it a source-routed random-walk.

@@

  \item We propose SphinxES, an extension of the
    \ac{Sphinx} mix-header format to set-based onion routing. SphinxES allows each layer of an onion route to contain several alternative next nodes, thus realizing a source-routed limited random-walk protocol.

  \item Building on SphinxES, we introduce the \ac{SPOR} %% node selection strategy for routing
    protocol
    that, given a secure 
    \ac{RPS} protocol and availability estimates, selects nodes to populate the 
    layers of SphinxES in order to maximize the availability of the route. This node selection procedure 
    yields reliable routes even in the presence of low-availability nodes while retaining the strong privacy properties of onion routing.

  \item We provide a protocol for a device \squad to estimate the availabilities 
    of its own devices, based on Markov models and \squad overlays.
    These estimated availabilities can then be exploited by \ac{SPOR} to populate SphinxES.
   % \commentDaniel{We should add some more details, maybe.}

@@

The remainder of this paper is organized as follows. Section~\ref{system-model} presents the
system and adversary models as well as the desired security and
privacy properties of \name. Section~\ref{approach} describes the
overall approach. In Section~\ref{SphinxES}, we introduce \sphinxes. 
Then, in Section~\ref{design}, we introduce the different building
blocks of \name. In sections~\ref{security-discussion} and \ref{Performance},
respectively, we evaluate the security and performance of our
approach. We set \name into context with related work in
Section~\ref{RelatedWork}, and finally conclude with Section~\ref{conclusion}.

### 2020-03-24 paper/spor.tex
Edits all forms of SphinxES, \Sphinxes, \ac{Sphinx} etc.

There are many uses of \Sphinxes, many criteria that can be used to select the 
nodes in each layer.
We will focus on maximizing availability when routing in a network with high 
churn, but one could equally well select nodes to maximize, \eg, bandwidth.
We now describe a protocol, \ac{SPOR}, which uses \Sphinxes to transfer messages 
from a source to a destination over a network of nodes with high churn.

\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item  \(\avail_d(t)\) is the node's probability of being online as a function of time. 
  Its computation will be discussed in~\ref{ssec:device_availability}.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}. Its function is analogous to 
Tor's authoritative directory servers, but we need a decentralized system. 
We will treat \(\avail_d\) in \cref{sec:squad_overlay}.

>>>>

There are many uses of SphinxES, many criteria that can be used to select the 
nodes in each layer.
We will focus on maximizing availability when routing in a network with high 
churn, but one could equally well select nodes to maximize, \eg, bandwidth.
We now describe a protocol, \ac{SPOR}, which uses SphinxES to transfer messages 
from a source to a destination over a network of nodes with high churn.

\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item  \(\avail_d(t)\) is the node's probability of being online as a function of time. 
  Its computation will be discussed in~\ref{ssec:device_availability}.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}. Its function is analogous to \acg{Tor} authoritative 
directory servers, but we need a decentralized system. We will treat 
\(\avail_d\) in \cref{sec:squad_overlay}.
